moderated_regressions

### 2024-04-25 moderated_regressions.Rmd
adding info for tables
finalizing numbers for tables

#r squared
summary(challenge_resource_burnout_model2)
summary(challenge_resource_burnout_model2)$coefficients[3, 1]

summary(challenge_resource_burnout_model3)
```

>>>>

#r squared
summary(challenge_resource_burnout_model2)
challenge_resource_burnout_model2_r <- summary(challenge_resource_burnout_model2)$r.squared
summary(challenge_resource_burnout_model3)
challenge_resource_burnout_model3_r <- summary(challenge_resource_burnout_model3)$r.squared

challenge_resource_burnout_r_square_change <- challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r
challenge_resource_burnout_r_square_change
